To do list for this paper

### 2018-08-15 PaperToDo.Rmd
lots of done things

- [X] Add another example of a data set for M-in-DS (Sect 4.1) (Congress)
- [ ] Make node-link gif available online
- [ ] Insert link to full node-link gif in paper
- [ ] Make adjmat gif available online
- [ ] Insert link to full adjmat gif in paper
- [ ] Beef up transition before Sect 4.4
- [X] Figure 6: reverse order of adjacency matrix y-axis
- [X] Figure 5: get rid of Vs on node labels, make font bigger
- [X] Figure 7 not showing up??
- [X] Fix error on p. 21 (probably related to above)
- [X] Heatmap p 23 missing caption
- [X] Describe Figure 8 more. What is going on??
- [X] Add geomnet example in 4.2
- [X] p. 26-28 figure refs & code is broken
- [X] Get rid of repeated plot p 29
- [X] p. 34 code is broken
- [X] General proof reading

>>>>

- [X] Add another example of a data set for M-in-DS (Sect 4.1) (Congress)
- [X] Make node-link gif available online
- [X] Insert link to full node-link gif in paper
- [X] Make adjmat gif available online
- [X] Insert link to full adjmat gif in paper
- [ ] Beef up transition before Sect 4.4
- [X] Figure 6: reverse order of adjacency matrix y-axis
- [X] Figure 5: get rid of Vs on node labels, make font bigger
- [X] Figure 7 not showing up??
- [X] Fix error on p. 21 (probably related to above)
- [X] Heatmap p 23 missing caption
- [X] Describe Figure 8 more. What is going on??
- [X] Add geomnet example in 4.2
- [X] p. 26-28 figure refs & code is broken
- [X] Get rid of repeated plot p 29
- [X] p. 34 code is broken
- [X] General proof reading
